Structures Report

### 2017-03-22 mu/structures-report/structures-report.tex
minimal changes
Starting bands
sab
Almost finishing report.
Making bands.

\usepackage{geometry}
\geometry{letterpaper, margin=2cm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}

@@

\section{Up} % (fold)
\label{sec:up}

@@

@@

@@

@@

@@

@@

\section{aa} % (fold)
\label{sec:aa}

@@

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.5:3.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-vxb-rtp.pdf}
    \includegraphics[width=0.7\textwidth]{altplots/alt-vyb-rtp.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:aa-rtp}
\end{figure}

@@

@@

\section{ab} % (fold)
\label{sec:ab}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvxb.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ for different
    polarization angles.}
    \label{fig:ab-magvxb}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-1.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 155$^{\circ}$.}
    \label{fig:ab-vxb}
\end{figure}

@@

% \begin{figure}[ht]
%     \centering
%     \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyx-layers.pdf}
%     \caption{Layer decomposition for the most intense response:
%     $\mathcal{V}^{\mathrm{yz}}$.}
%     \label{fig:aa-lay}
% \end{figure}

@@

>>>>

\usepackage{geometry}
\geometry{letterpaper, margin=2cm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[inline  ]{showlabels}

@@

\section{Up (graphone)} % (fold)
\label{sec:up}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.45\textwidth]{../up/up-figures/up-1}
    \includegraphics[width=0.45\textwidth]{../up/up-figures/up-2}
    \caption{Up structure}
    \label{fig:upstruc}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-1.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:up-xbybcomp-1}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{upplots/up-absvab-2.pdf}
    % \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:up-xbybcomp-2}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.45\textwidth]{../alt/alt-figures/alt-1}
    \includegraphics[width=0.45\textwidth]{../alt/alt-figures/alt-2}
    \caption{Alt structure.}
    \label{fig:altstruc}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{altplots/alt-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$}    
    \label{fig:alt-xbybcomp}
\end{figure}

@@

\section{HNBC$_{2}$H-aa} % (fold)
% \label{sec:aa}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.3\textwidth]{../hnbGh-aa/hnbGh-aa-figures/hnbGh-aa-2}
    \caption{HNBC$_{2}$H-aa structure}
    \label{fig:aastruc}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%% |V^{ab}| [0.5:3.0] rtp comp %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{$|\mathcal{V}^{\mathrm{ab}}|$, angles
$\theta$ and $\varphi$, layers, and comparison with CdSe and GaAs.}
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vxb-rtp.pdf}
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-vyb-rtp.pdf}
    \caption{$|\mathcal{V}^{\mathrm{ab}}|$ (solid line, leftside scale) and the
    corresponding angles $\theta$ and $\varphi$ (dashed lines, rightside scale).}
    \label{fig:aa-rtp}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{aaplots/hnbGh-aa-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$.}    
    \label{fig:aa-xbybcomp}
\end{figure}

@@

\section{HNBC$_{2}$H-ab} % (fold)
\label{sec:ab}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.3\textwidth]{../hnbGh-ab/hnbGh-ab-figures/hnbGh-ab-2}
    \caption{HNBC$_{2}$H-ab structure}
    \label{fig:abstruc}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-magvxb.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ for different
    polarization angles.}
    \label{fig:ab-magvxb}
\end{figure}
\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-ab-vxb.pdf}
    \caption{Three components of $\mathcal{V}^{\mathrm{xb}} $ @ 155$^{\circ}$.}
    \label{fig:ab-vxb}
\end{figure}

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.7\textwidth]{abplots/hnbGh-absvab.pdf}
    \caption{Comparisson of $|\mathcal{V}^{\mathrm{xb}}|$ and $|\mathcal{V}^{\mathrm{yb}}|$.}    
    \label{fig:ab-xbybcomp}
\end{figure}
